### 2021-10-12 README.Rmd
Cpue cs (#5)
* interesting. open access now works

* safety stop, things working but tricky to think through optimization

* testing reverse optimization

* adding in hyperallometry

* revised version focused on bycatch

>>>>

# idea for fleet revamp

I think the most straightforward route is just to build a bit more realism in.

1. Burn the model in

2. Calculate costs such that profit per unit effort is 0, where costs are calculated based on f, not effort.

3. Redistribute effort, and going forward use open access dynamics. So, if you set that up right, there will now be a tradeoff between increased catch from effort concentration but also increased cost from f approaching 1.

Worth a shot

q <- 0.1

m <- 0.2

effort <- seq(0,100, by = 1)

f <- effort * q

b <- 100

price <- 10

catch <- f / (f + m) * b * (1 - exp(-(f + m)))

biomass <- b * (exp(-(f + m)))

revenue <- catch * price

cost = effort^2

plot(revenue - cost)

plot(revenue)

f <- 10 * q

r1 <- 2 * (f / (f + m) * b * (1 - exp(-(f+ m))) * price - 10^2)

f <- 20 * q

r2 <- (f / (f + m) * b * (1 - exp(-(f+ m))) * price - 20^2)

r1

r2

```
 Yeah that checks out. So, the idea is what? Run the population to equilibrium, and then find a cost coefficient such that system-wide profits are zero

q <- 0.1

m <- 0.2

effort <-10

f <- effort * q

b <- 100

price <- 10

cost <- 10

max_delta <- 0.25

cost = (f / (f + m) * b * (1 - exp(-(f+ m))) * price) / effort^2

p1 <- (f / (f + m) * b * (1 - exp(-(f+ m))) * price) - cost * effort^2

theta = log((effort * (1 + max_delta)) / effort) / (f / (f + m) * b * (1 - exp(-(f+ m))) * price)

e2 <- effort * exp(theta * (f / (f + m) * b * (1 - exp(-(f+ m))) * price))

e2 / effort - 1

e2 <- effort * exp(theta * (10000))

e2 / effort

# so what if you tuned it so that if you caught all of ssb0 it would go up by 25%
```

 What about a sigmoid form, so that it's symetric in increase vs decrease?

p = seq(-10,10)

x = 1.25 * (1 / (1 + exp(-p)))

plot(p,x)
